Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-14 analysis/paper/paper.Rmd
edit compendium availability statement
Add statement of contributions

# Authors' contributions

@@

All code used in the analyses and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
A browsable webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.

>>>>

# Authors' contributions
A.H.S, E.DP, Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S, E.DP, Z.F. and K.dSA evaluated articles for scoring.
A.H.S. designed the computational framework with feedback from E.DP and Z.F.
A.H.S wrote the manuscript in consultation with E.DP.
All authors provided critical feedback and helped contribute to the final version of the manuscript.

@@

All code used in the analyses and data visualization and associated materials have been made available as research compendium available from DOI [https://doi.org/10.5281/zenodo.1250664](10.5281/zenodo.1250664).
A webpage version of the compendium is available from <https://openplantpathology.github.io/Reproducibility_in_Plant_Pathology/>.
